19Q2

### 2020-01-12 19Q2.Rmd
reconfigured KS test -- no tests were signif, sent to Dan for input

## KS tests

**1/10/20: Restrict datasets to heatmap drug-genes and run KS tests.**
```{r}
ks.test(filter(ccle_signif_g2p_dg, InG2P == "Yes")$p, filter(ccle_signif_g2p_dg, InG2P == "No")$p)
ks.test(filter(ctrp_signif_g2p_dg, InG2P == "Yes")$p, filter(ctrp_signif_g2p_dg, InG2P == "No")$p)
ks.test(filter(gdsc_signif_g2p_dg, InG2P == "Yes")$p, filter(gdsc_signif_g2p_dg, InG2P == "No")$p)

ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)
ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)
ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)

ks.test(filter(ccle_signif_prot, InG2P == "Yes")$p, filter(ccle_signif_prot, InG2P == "No")$p)
ks.test(filter(ctrp_signif_prot, InG2P == "Yes")$p, filter(ctrp_signif_prot, InG2P == "No")$p)
ks.test(filter(gdsc_signif_prot, InG2P == "Yes")$p, filter(gdsc_signif_prot, InG2P == "No")$p)

ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)
ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)
ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)

ks.test(filter(cn_cor, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CCLE" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "CTRP" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor, Dataset == "GDSC" & InG2P == "No")$CN_p)

ks.test(filter(ge_cor, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CCLE" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "CTRP" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor, Dataset == "GDSC" & InG2P == "No")$GE_p)

ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)
ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_r, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)

ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)
ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)
```

@@

```{r}
crispr_g2p_count <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
ccle_g2p_count <- filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
ctrp_g2p_count <- filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
gdsc_g2p_count <- filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
```

```{r mutation_figure, eval=FALSE}
mut_genes <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Gene, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Gene), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Gene)
mut_drugs <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Drug, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Drug), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Drug)

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_mut_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

```{r, eval=FALSE}
ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")

@@

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs), feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_prot_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
# Copy number
cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)

@@

@@

```{r}
g2p_disease_colors

gdsc_signif_prot_summ <- filter(gdsc_signif_prot, InG2P == "Yes") 
ctrp_prot_filt <- filter(ctrp_prot, Drug_Gene_Protein_Change %in% filter(ctrp_signif_prot_summ, p < 0.05)$Drug_Gene_Protein_Change)

# ccle_prot_annot <- select(filter(ccle_prot, Drug_Gene %in% ccle_mut_lin_filt$Drug_Gene & Change_Status == "Yes"), Drug_Gene, Protein_Change, DepMap_ID) 
# test <- merge(ccle_mut_lin_filt, ccle_prot_annot, by = c("DepMap_ID", "Drug_Gene"), all.x = TRUE)
```

>>>>

@@

```{r mut_ks_tests}
mut_genes <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Gene, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Gene), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Gene)
mut_drugs <- union(union(filter(ccle_signif_g2p_dg, InG2P == "Yes")$Drug, filter(ctrp_signif_g2p_dg, InG2P == "Yes")$Drug), filter(gdsc_signif_g2p_dg, InG2P == "Yes")$Drug)

ccle_mut_ht_dat <- filter(ccle_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)

ctrp_mut_ht_dat <- filter(ctrp_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)

gdsc_mut_ht_dat <- filter(gdsc_signif_g2p_dg, Drug %in% mut_drugs & Gene %in% mut_genes)
ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)
```

```{r mutation_figure, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_mut_ht_dat, feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_mut_ht_dat, feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = , feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_mut_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

```{r prot_ks_tests}
ccle_prot$disease_g2p <- ifelse(ccle_prot$disease %in% g2p_diseases, ccle_prot$disease, "other")
ctrp_prot$disease_g2p <- ifelse(ctrp_prot$disease %in% g2p_diseases, ctrp_prot$disease, "other")
gdsc_prot$disease_g2p <- ifelse(gdsc_prot$disease %in% g2p_diseases, gdsc_prot$disease, "other")

@@

ccle_prot_ht_data <- filter(ccle_signif_prot_4plot, Drug %in% prot_drugs)
ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)

ctrp_prot_ht_data <- filter(ctrp_signif_prot_4plot, Drug %in% prot_drugs)
ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)

gdsc_prot_ht_data <- filter(gdsc_signif_prot_4plot, Drug %in% prot_drugs)
ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)
```

```{r, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = , feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = , feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = , feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 3, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_prot_list <- ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

```{r cn_ge_ks_tests}
cn_genes <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Gene)
cn_drugs <- unique(filter(cn_cor, Dataset != "CRISPR" & InG2P == "Yes")$Drug)

ccle_cn_ht_data <- filter(cn_cor, Dataset == "CCLE" & Drug %in% cn_drugs & Gene %in% cn_genes)
ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)
ctrp_cn_ht_data <- filter(cn_cor, Dataset == "CTRP" & Drug %in% cn_drugs & Gene %in% cn_genes)
ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)
gdsc_cn_ht_data <- filter(cn_cor, Dataset == "GDSC" & Drug %in% cn_drugs & Gene %in% cn_genes)
ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)

ccle_ge_ht_data <- filter(ge_cor, Dataset == "CCLE" & Drug %in% ge_drugs & Gene %in% ge_genes)
ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)
ctrp_ge_ht_data <- filter(ge_cor, Dataset == "CTRP" & Drug %in% ge_drugs & Gene %in% ge_genes)
ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)
gdsc_ge_ht_data <- filter(ge_cor, Dataset == "GDSC" & Drug %in% ge_drugs & Gene %in% ge_genes)
ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)
```

```{r CN_GE_fig, eval=FALSE, fig.height=10, fig.width=15}
# Copy number

@@

```{r pancan_ks_res}
pancan_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
  "p.value" = c(ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)$p.value,
  ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)$p.value,
  ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)$p.value))
```

@@

```{r lineages_ks_tests, warning=FALSE}
ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value
ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value
ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value

ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value
ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value
ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value

ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value
ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value
ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value

ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value
ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value
ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value

lineage_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
  "p.value" = c(ks.test(filter(ccle_signif_dgl, InG2P == "Yes")$p, filter(ccle_signif_dgl, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_signif_dgl, InG2P == "Yes")$p, filter(ctrp_signif_dgl, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_signif_dgl, InG2P == "Yes")$p, filter(gdsc_signif_dgl, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_signif_prot_lin, InG2P == "Yes")$p, filter(ccle_signif_prot_lin, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_signif_prot_lin, InG2P == "Yes")$p, filter(ctrp_signif_prot_lin, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_signif_prot_lin, InG2P == "Yes")$p, filter(gdsc_signif_prot_lin, InG2P == "No")$p)$p.value,
  ks.test(filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CCLE" & InG2P == "No")$CN_p)$p.value,
  ks.test(filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "CTRP" & InG2P == "No")$CN_p)$p.value,
  ks.test(filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$CN_p, filter(cn_cor_lin, Dataset == "GDSC" & InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CCLE" & InG2P == "No")$GE_p)$p.value,
  ks.test(filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "CTRP" & InG2P == "No")$GE_p)$p.value,
  ks.test(filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "Yes")$GE_p, filter(ge_cor_lin, Dataset == "GDSC" & InG2P == "No")$GE_p)$p.value))
```
